Autocorrelation in Sparse Distributed Memory

### 2019-06-30 paperIEEE.tex
macbookpro compiling

% !TEX root = ../partial-sdm.tex

@@

\begin{IEEEbiography}[
  {
  \includegraphics[width=1in,height=1.25in,clip]{./Chapters/Linhares.jpg}
  }
  ]
{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published ~30 papers in journals such as \emph{Artificial Intelligence, Biological Cybernetics, Cognitive Science, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Human Neuroscience,} etc.
\end{IEEEbiography}

>>>>

@@

\begin{IEEEbiography}[
  {
  \includegraphics[width=1in,height=1.25in,clip]{./Chapters/Linhares.jpg}
  }
  ]
{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published ~30 papers in journals such as \emph{Artificial Intelligence, Applied Intelligence, Biological Cybernetics, Cognitive Science, Cognitive Systems Research, Computers & Operations Research, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Human Neuroscience,} among others.
\end{IEEEbiography}
